CL-PFU: A suite of R packages for energy conversion chain analysis

### 2023-08-17 paper.Rmd
Updates to example.

```{r, eval=FALSE}
# (1) Purchase, download, and store IEA data in correct location.
# (2) Download FAO and ILO data for muscle work calculations
# via the included script.
# This download is needed only once and
# the results are now stored in the repository. 
source(file.path("ExampleFolder", "DownloadScripts", "download_mw_data.R"))
```

```{r, eval=FALSE}
# (3) Run the PFUDatabase pipeline
targets::tar_make(script = file.path("ExampleFolder", "_targets_pfudatabase.R"))
# (4) Run the PFUAggDatabase pipeline
targets::tar_make_future(script = file.path("ExampleFolder", "_targets_pfuaggdatabase.R"),
                         workers = 4)
```

```{r}
# (5) Review results using the saved pins
# Establish the pinboard
pinboard <- file.path("ExampleFolder", "OutputData", "PipelineReleases") |> 
  pins::board_folder(versioned = TRUE)
# Look at the psut data frame
# created by the PFUDatabase pipeline
psut <- pinboard |>
  pins::pin_read("psut", version = "20230811T122618Z-3b7b3")
head(psut)
# Each column of the psut data frame contains sparse matrices.
colnames(psut$R[[1]])
psut$R[[1]]

# Look at the aggregate PFU efficiency data frame
# created by the PFUAggDatabase pipeline
agg_eta_pfu <- pinboard |> 
  pins::pin_read("agg_eta_pfu", version = "20230817T180346Z-45741")
agg_eta_pfu |> 
  # Filter and delete columns 
  # to present a subset of exergy results in a data frame
  dplyr::filter(Energy.type == "X", IEAMW == "Both", 
                Product.aggregation == "Specified", 
                Industry.aggregation == "Specified", 
                GrossNet == "Net",
                Country %in% c("GHA", "ZAF")) |> 
  dplyr::mutate(
    Method = NULL, 
    Energy.type = NULL,
    Product.aggregation = NULL,
    Industry.aggregation = NULL,
    IEAMW = NULL,
    Chopped.mat = NULL, 
    Chopped.var = NULL, 
    GrossNet = NULL
  )
```

>>>>

```{r, eval=FALSE}
# (1) Purchase, download, and store IEA data in correct location.
#     Sample data are provided at the correct location in the repository.
# (2) Download FAO and ILO data for muscle work calculations
#     via the included script.
#     This download step is needed only once and
#     the data are stored in the repository.
source(file.path("ExampleFolder", "DownloadScripts", "download_mw_data.R"))
```

```{r, eval=FALSE}
# (3) Run the PFUDatabase pipeline to create RUVY matrices.
targets::tar_make(script = file.path("ExampleFolder", "_targets_pfudatabase.R"))
# (4) Run the PFUAggDatabase pipeline to aggregate 
#     energy and calculate efficiencies..
targets::tar_make_future(script = file.path("ExampleFolder", "_targets_pfuaggdatabase.R"),
                         workers = 4)
```

```{r}
# (5) Review results using saved pins, which are stored in the repository.
#     Establish the pinboard.
pinboard <- file.path("ExampleFolder", "OutputData", "PipelineReleases") |> 
  pins::board_folder(versioned = TRUE)
#     Look at the psut data frame
#     created by the PFUDatabase pipeline.
psut <- pinboard |>
  pins::pin_read(name = "psut", version = "20230811T122618Z-3b7b3")
head(psut)
#     Each column of the psut data frame contains sparse matrices, 
#     the columns of which are suppressed on display.
#     Show the column names here.
colnames(psut$R[[1]])
#     Show an example resource matrix.
psut$R[[1]]

#     Review the aggregate PFU efficiency data frame
#     created by the PFUAggDatabase pipeline.
agg_eta_pfu <- pinboard |> 
  pins::pin_read(name = "agg_eta_pfu", version = "20230817T180346Z-45741")
agg_eta_pfu |> 
#     Filter and delete columns 
#     to present a subset of exergy results in a data frame.
#     The EX.p, EX.f, and EX.u columns contain aggregate exergy at
#     primary, final, and useful stages, respectively, in TJ.
#     The eta_pf, eta_fu, and eta_pu columns contain aggregate
#     primary-to-final, final-to-useful, and 
#     primary-to-useful efficiencies.
  dplyr::filter(Energy.type == "X", IEAMW == "Both", 
                Product.aggregation == "Specified", 
                Industry.aggregation == "Specified", 
                GrossNet == "Net",
                Country %in% c("GHA", "ZAF")) |> 
  dplyr::mutate(
    Method = NULL, 
    Energy.type = NULL,
    Product.aggregation = NULL,
    Industry.aggregation = NULL,
    IEAMW = NULL,
    Chopped.mat = NULL, 
    Chopped.var = NULL, 
    GrossNet = NULL
  )
```
